The complex structure and peculiar internal motions of the planetary nebula NGC 6210

### 2020-03-16 ms.tex
Add the table and figure of the 3d reconstruction

@@

\begin{figure}
  \includegraphics[width=\linewidth]
  {talk-figs/turtle-talk-morelia-2020-02-export-011}
  \caption{Place-holder figure for three-dimensional reconstruction}
  \label{fig:axis-B-3d}
\end{figure}

\subsection{Flow axes}
\label{sec:flow-axes}

\begin{figure}
  \includegraphics[width=\linewidth]
  {talk-figs/turtle-talk-morelia-2020-02-export-010}
  \caption{Place-holder figure for Axis A and B}
  \label{fig:flow-axes-AB}
\end{figure}

\begin{figure}
  \includegraphics[width=\linewidth]
  {talk-figs/turtle-talk-morelia-2020-02-export-014}
  \caption{Place-holder figure for all four axes.}
  \label{fig:flow-axes-ABCD}
\end{figure}

>>>>

\begin{table*}
  \caption{Components in three dimensions}
  \label{tab:3d}
  \centering
  \setlength\tabcolsep{5pt}
  \sisetup{
    table-format = >2.1(1),
    table-auto-round,
  }
  \begin{tabular}{
    l % System
    r % PA
    r % Axis
    S[table-format = >2.0(1)] % Vlos
    S % Vpos
    S % V
    S % i
    S % Rproj
    S % R
    S % t
    }
    \toprule
    {System} & {PA} & {Axis} & {\(V_\text{los}\)} &  {\(V_\text{pos}\)} &  {\(V_\text{tot}\)} & {\(i\)} & {\(R_\text{proj}\)} & {\(R\), pc} & {\(t\), 1000 yr}\\
    \midrule
    Inner shell A NNW & 340 & A\(^+\) & +8 \pm 3 & 48. \pm 7. & 49. \pm 7. & 11. \pm 4. & 7.0 \pm 0.5 & 7.1 \pm 0.5 & 1.4 \pm 0.2\\
    Outer lobe I+/VII+ & 340 & A\(^+\) & +28 \pm 2 & 82. \pm 29. & 89. \pm 27. & 22. \pm 7. & 16.0 \pm 1 & 17.3 \pm 1.4 & 1.9 \pm 0.7\\
North knot & 340 & A\(^+\) & +24 \pm 1 & 60. \pm 4. & 67. \pm 4. & 26. \pm 2. & 17. \pm 1 & 18.9 \pm 1.2 & 2.7 \pm 0.2\\
Inner shell A SSE & 160 & A\(^-\) & -17 \pm 3 & 51. \pm 7. & 55. \pm 7. & -22. \pm 4. & 6.5 \pm 0.5 & 7.0 \pm 0.6 & 1.2 \pm 0.2\\
Outer lobe I- & 160 & A\(^-\) & -32 \pm 1 & 71. \pm 29. & 81. \pm 26. & -28. \pm 10. & 15. \pm 2 & 17.0 \pm 2.8 & 2.0 \pm 0.8\\
Outer lobe VIII- & 160 & A\(^-\) & -10 \pm 1 & 67. \pm 9. & 68. \pm 9. & -10. \pm 2. & 23. \pm 1 & 23.4 \pm 1.0 & 3.2 \pm 0.4\\
Outer lobe II+ & 170 & C\(^+\) & +24 \pm 2 & 58. \pm 12. & 65. \pm 11. & 26. \pm 5. & 24. \pm 1 & 26.7 \pm 1.6 & 3.9 \pm 0.9\\
    Outer lobe II- & 355 & C\(^-\) & -25 \pm 3 &   & > 25.0 & < 0.0 & 21. \pm 3 & > 21.0 & \\
\addlinespace
Inner shell B ENE & 65 & B\(^-\) & -25 \pm 3 & 31. \pm 5. & 43. \pm 4. & -44. \pm 6. & 4. \pm 1 & 5.6 \pm 1.5 & 1.2 \pm 0.4\\
NE Blue complex & 60 &  & -51 \pm 1 & 23. \pm 5. & 65. \pm 2. & -69. \pm 4. & 5. \pm 1 & 14.0 \pm 3.8 & 2.1 \pm 0.6\\
IS ENE & 50 & B\(^-\) & -18 \pm 3 & 27. \pm 15. & 35. \pm 12. & -39. \pm 16. & 9. \pm 2 & 11.6 \pm 3.7 & 3.2 \pm 2.0\\
Inner shell B WSW & 240 & B\(^+\) & +18 \pm 3 & 29. \pm 4. & 36. \pm 4. & 37. \pm 6. & 4.5 \pm 1 & 5.6 \pm 1.3 & 1.5 \pm 0.4\\
IS WSW & 260 & B\(^+\) & +20 \pm 3 & 29. \pm 26. & 38. \pm 20. & 40. \pm 26. & 11.5 \pm 1 & 15.0 \pm 5.9 & 3.8 \pm 3.5\\
SW Red complex & 250 &  & +38 \pm 1 & 18. \pm 3. & 49. \pm 2. & 68. \pm 3. & 7. \pm 2 & 18.7 \pm 5.9 & 3.7 \pm 1.2\\
N(E) Red complex & 30 &  & +25 \pm 2 & 5. \pm 4. & 30. \pm 2. & 81. \pm 7. & 4. \pm 1 & 25.6 \pm 20.7 & 8.0 \pm 6.7\\
SW Faint Blue & 225 &  & -26 \pm 1 & 26. \pm 4. & 41. \pm 3. & -50. \pm 4. & 7. \pm 1 & 10.9 \pm 1.8 & 2.6 \pm 0.5\\
\addlinespace
Outer lobe X+ & 285 & D+ & +6 \pm 2 & 48. \pm 43. & 49. \pm 43. & 9. \pm 8. & 18.5 \pm 1.5 & 18.7 \pm 1.6 & 3.7 \pm 3.3\\
Outer lobe IV+ & 315 & D+ & +13 \pm 1 & 33. \pm 7. & 37. \pm 6. & 25. \pm 5. & 10. \pm 1 & 11.0 \pm 1.2 & 2.9 \pm 0.6\\
NW knot ([N II]) & 310 &  & +18 \pm 1 & 11. \pm 8. & 24. \pm 4. & 63. \pm 17. & 8. \pm 1 & 17.6 \pm 10.5 & 6.7 \pm 4.5\\
N(W) Red complex & 300 &  & +21 \pm 2 & 10. \pm 4. & 27. \pm 3. & 68. \pm 8. & 6. \pm 2 & 16.0 \pm 7.7 & 6.0 \pm 3.1\\
Outer lobe X-/IV-/V+ & 120 & D- & -8 \pm 4 & 24. \pm 14. & 26. \pm 13. & -22. \pm 15. & 13. \pm 3 & 14.0 \pm 3.6 & 5.2 \pm 3.3\\
    SE Blue complex & 135 &  & -31 \pm 3 & 39. \pm 10. & 54. \pm 8. & -44. \pm 8. & 4.5 \pm 1 & 6.3 \pm 1.6 & 1.1 \pm 0.4\\
    \bottomrule
\end{tabular}
\end{table*}

@@

\begin{figure*}
  \includegraphics[width=\linewidth]
  {figs/cut-axis-4panel}
  \caption{Three dimensional reconstruction of the nebular structure and kinematics. }
  \label{fig:cut-axis-3d}
\end{figure*}
